\section{Glossary - either before report or after report -breaks reading flow!}
\section{Introduction - Frame it as a video IoT problem. IoT is nice but video in IoT is hard to manage especially live data. How to cope with a lot of real time data examplified in the leading video surveilance company.}
\subsection{Motivation - More reference; Less technical --> building better scalability and flexbility, modular vs monolithic, cloud --> Don't be so technical, more highlevel and grandual go into real challenges}
\subsection{Problem Definition}
\section{Methodology - Could also be in Introduction (if more than 1 page)}
\section{Motivate why Cloud is important to milestones --> Enabling surveilance in the cloud. Collecting data from video cameras and building flexible scaling service architecture around that, that can be extended upgraded to add functionalty and maintainability. Service Mesh is relevant for Milestone.}
\section{History of Microservice Architecture - integrate SOA from paper - lose coupling!!! using descriptive messages rather de; microservice came from SOA; Network function virtualization and software defined network (only look at it)}
\section{State of the Art (Competitor analysis)}
\section{Literature Review/ What is a Service Mesh --> merge with history}

\section{Requirements from Milestone}
\subsection{Interviews (Head of Research and Cloud Orchestration Lead + With Professional from Istio Gathering in Cph)} 
\subsection{Functional Requirements ; Each Req should have source and reason}
\subsection{Non-Functional Requirements; source and reason}
\subsection{MoSCoW --> Give reason for prioritize certain feature (discuss what I can do and lower priority could be part for future.}
\section{Istio}
\subsection{Capabilities - Consider removing this. }
\subsection{Testing Istio Overhead in a Generic Setup}

\section{Implementation in Milestone}
\subsection{The current C2C? setup at Milestone}
\subsection{Platform Improvements from Istio}
\subsection{Chaos Testing}
\subsection{Benchmarking before vs after}
\section{Reflection/ Evaluation}
\section{Future Work}
\section{Conclusion}




