\subsubsection{Containers} \label{sec:containers}
Containers first surfaced in 2007 with the release of Linux Containers (LXC). They provide an abstraction and isolation layer to the software inside, hence the name containers. Basically, a container is packaged software that runs independent from the underlying system. They are created at runtime from container images, which are packaged, standalone executable software including everything the main application needs to run (code, runtime, system tools, libraries and settings)\cite{containerDefinition:online}. Containers offer
"unprecedented agility in developing and running applications in cloud environment especially when combined with a microservice-style architecture."\cite{microserviceContainers} Since their inception there has been considered development of containers, especially by Docker, a company developing the same named application which is often used synonymously for containers. Docker donated its main container runtime environment, called containerd, to the CNCF open source community and later, in late 2017, announced the first major release of containerd\footnote{See \url{https://blog.docker.com/2017/12/cncf-containerd-1-0-ga-announcement/} for more information on this topic}. Containerd is becoming rapidly the industry norm as the runtime was already widely used when it belonged to Docker.

Today, containers are the building blogs of the cloud and power almost all distributed applications. Craig McLuckie, the lead product manager cloud computing product at Google, said in a panel discussion during the Linux collaboration summit in Febraury 2015:
\begin{displayquote}
\textit{\textbf{\large{``}}}
\textit{This containers revolution is changing the basic act of software consumption. It’s redefining this much more lightweight, portable unit, or atom, that is much easier to manage... It’s a gateway to dynamic management and dynamic systems.}
\textit{\textbf{\large{''}}}
\end{displayquote}
It is important to note, that while the cloud saw the first transformation from containers, the edge is part of the same dynamic system and stands to profit enormously from adapting containers. They offer many advantages over conventional deployments but have their drawbacks. For the edge resource consumption, hardware access and security are especially important and explained in more detail.\footnote{To keep the thesis concise I will not explain how containers work in greater detail only when required for the understanding of the content. For more information see Docker's website  \url{https://www.docker.com/resources/what-container} and containerd \url{https://containerd.io/}}.\\[0.5mm]

% \vspace{0.5mm} \ \\
\textbf{\textit{Resource Consumption}}\\
\input{sections/2-extendedSota/containers/resourceConsumption.tex}

% \vspace{0.5mm} \ \\
\textbf{\textit{Hardware Access}}\\
\input{sections/2-extendedSota/containers/hardwareAccess.tex}

% \vspace{0.5mm} \ \\
\textbf{\textit{Security}}\\
\input{sections/2-extendedSota/containers/security.tex}



\comment{
https://www.iotforall.com/containers-on-the-edge/

 They isolate the application runtime and the 

Containers and Cloud: From LXC to Docker to Kubernetes

%  try use if vspace does not work \\[0.5mm]
}
