% Please add the following required packages to your document preamble:
% \usepackage[normalem]{ulem}
% \useunder{\uline}{\ul}{}
% \begin{table}[]
\clearpage
\setlength\LTleft{-2.5cm}
\begin{longtable}{l p{1.5cm} l p{4cm} p{2cm} p{4cm} l }
\multicolumn{7}{l}{Functional Requirements}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \\
ID  & Name                                    & Classification & Description                                                                                                                                                                                & Solution                 & Reason                                                                                                                                                                                                                         & Source (section)                   \\ \hline
101 & Isolated applications                   &                & Each application has to function on its own. It has to handle database errors and communication errors in a non fatal way.                                                                 & Microservices            & Microservices enable a the separation of concern between applications.                                                                                                                                                         & \cref{cotnainers} \\
102 & Isolation to host computer              &                & The application has to be as isolated from the host environment as possible.                                                                                                               & Containers               & Containers with minimal access rights to host resources                                                                                                                                                                        & \textbackslash{}cref\{containers\} \\
103 & Minimal dependencies                    &                & The application has to have minimal runtime dependencies. If the application is built on the edge device, the compile time dependencies have to be minimal as well.                        & Compiled language        & Compiled languages put all their code dependencies inside                                                                                                                                                                      & \textbackslash{}cref\{containers\} \\
104 & Cross compilation                       &                & The edge applications need to be able to be cross-compiled.                                                                                                                                & GCC supportive language  & GCC supports a wide variety of architectures and is well maintained                                                                                                                                                            & \textbackslash{}cref\{containers\} \\
105 & Small images                            &                & The footprint of the application has to be small.                                                                                                                                          & Scratch Container        & The scratch container is empty and thus perfect for minimal builds.                                                                                                                                                            & \textbackslash{}cref\{containers\} \\
106 & Use different users                     &                & Each application should be run by different users. If one userspace is compromised it does not effect the other applications.                                                              & Containers               & Containers isolate by default the userspace on each container.                                                                                                                                                                 & \textbackslash{}cref\{containers\} \\
107 & Use non root user                       &                & The application should not run with root priviledges, except when really needed.                                                                                                           & Unpriviledged user       & An unpriviledged user is not able to access and/or modify system resources.                                                                                                                                                    & \textbackslash{}cref\{containers\} \\
108 & Isolate the application context         &                & The application process has to be isolated. Only if the application must access host resources should they be available to the application.                                                & Containers               & Containers isolate the process tree, network and filessystem per default. A container only has access to the resources in its namespace and cannot get access resources in another namespace, except when explicilty declared. & \textbackslash{}cref\{containers\} \\
109 & Secured application code                &                & The application source code needs to be secure in case of a databreach on the node. A malicious attacker should not be able to reconstruct the source code even when he gets access to it. & Compiled language        & Compiled languages generates machine code from source code. Machine code is very hard to decompile. Interpreted languages often obfuscated the compiled code, but compiled languages are usually deemed more secure.           & \textbackslash{}cref\{containers\} \\
110 & Trusted applications                    &                & The edge application needs to be verified before the deployment.                                                                                                                           & Cryptographic hashing    & If an application has a fixed size and other static characteristics, it is possible to make a cryptographic secure hash, so that the edge device can ensure, that the application is indeed the correct one.                   & \textbackslash{}cref\{containers\} \\
111 & Centralized orchestration               &                & The operator should only need to tell a central configuration tool in the cloud how the system should look like. The cloud should then orchestrate the edge automatically.                 & Kubernetes               & Kubernetes is split into masters, running the control plane, and workers, excecuting business related applications. The masters instrument the workers. A edge node could be modeled as a worker.                              & \textbackslash{}cref\{kubernetes\} \\
112 & Automatic application deployment        &                & Based on a new configuration, the edge device has to be able to automatically get a copy of the new application, shut down the old application and deploy the new one.                     & Kubernetes               & The Kubernetes master tells a worker what its desired state is. The worker will automatically work towards fulfilling the desired state.                                                                                       & \textbackslash{}cref\{kubernetes\} \\
113 & Isolate edge from cloud                 &                & The cloud and the edge should work independently, so without a data connection. This is in case the edge is powerful enough to run its own control plane.                                  & Multi-cluster            & Multi-cluster setups allow to split control planes between multiple clusters.                                                                                                                                                  & \textbackslash{}cref\{kubernetes\} \\
114 & Isolated cloud environments             &                & Developers should only have access to the resources they need.                                                                                                                             & Namespaces               & Kubernetes offers the concept of namespaces. They are a virtual cluster and thus allow the isolation of resources and RBAC.                                                                                                    & \textbackslash{}cref\{kubernetes\} \\
115 & Resource quotas                         &                & The operators must be able to set resource quotas on applications and groups of applications.                                                                                              & Kubernetes               & Kubernetes allows resource allocation based on applications (pods) and namespaces.                                                                                                                                             & \textbackslash{}cref\{kubernetes\} \\
116 & ARM compatible edge                     &                & The orchestration tool on the edge has to be able to run on a slower ARM powered devices.                                                                                                  & K3s                      & K3s was specifically developed to cope with resource limitted devices.                                                                                                                                                         & \textbackslash{}cref\{kubernetes\} \\
117 & Node fault tolerance                    &                & The state of each node should be synchronized in the system, so that in case of an error, the last operable state can be recovered                                                         & Kubernetes               & The master synchronizes the state of its workers in a pre-set interval. If a worker goes down, the master can fully reconstruct the state on the same device or on another device (locally stored data is then lost however).  & \textbackslash{}cref\{kubernetes\} \\
118 & Decentralized edge storage              & Would          & When possible each edge device should synchronization important data with other edge devices in a distributed database.                                                                    & Distributed database     & Use a distributed database on multiple nodes. The CNCF provides a list of cloud native database here \textbackslash{}url\{https://landscape.cncf.io/category=cloud-native-storage\&format=card-mode\&grouping=category\}       & \textbackslash{}cref\{kubernetes\} \\
119 & Traffic prioritization                  &                & System critical information has to be prioritized.                                                                                                                                         & Istio                    & Istio is able to fine tune the communication between services. This enables to                                                                                                                                                 & \textbackslash{}cref\{kubernetes\} \\
120 & Whitelist connections                   &                & Only allow certain IPs to access the nodes. This allows for fain grained remote access control.                                                                                            & Multi-cluster with Istio & The Istio gateway can filter on a wide variety of parameters, including whitelisting certain IPs.                                                                                                                              & \textbackslash{}cref\{kubernetes\} \\
121 & Application independent traffic shaping & Should         & The traffic shaping has to be contralable without changing the application code.                                                                                                           & Istio                    & Istio can reroute traffic, change retries, headers based on services.                                                                                                                                                          & \textbackslash{}cref\{edgeIoT\}    \\
122 & Secure traffic within cluster           & Should         & The communication inside the cluster has to be secure. This includes the edge to cloud communication.                                                                                      & Istio                    & With Istio it is possible to encrypt the communication between pods, without encrypting the actual communication. This ensures that at any point in time, the communication between the edge and the cloud is secure.          & \textbackslash{}cref\{edgeIoT\}    \\
123 & Internet compatible IoT protocol        & Must           & The IoT protocol needs to be compatible with the Internet protocol. This enables addressing of IoT devices through the Internet in case of a static IP.                                    & CoAP                     & CoAP works with UDP packages and is thus compatible with the Internet.                                                                                                                                                         & \textbackslash{}cref\{edgeIoT\}    \\
124 & Secure traffic with IoT devices         & Could          & The communication between the IoT gateway/edge device and the IoT device needs to be secure.                                                                                               & CoAP with DTLS           & CoAP supports the DTLS standard for end-to-end encryption.                                                                                                                                                                     & \textbackslash{}cref\{edgeIoT\}    \\
125 & Efficient message compression           & Should         & The messages between the edge device and the IoT device need to be efficiently compressed to save resource and enhance speed.                                                              & Protobufs                & Protobufs offer a very small compression algorithm.                                                                                                                                                                            & \textbackslash{}cref\{edgeIoT\}    \\
126 & Energy efficient transmission           & Should         & The transmission between the edge and the IoT device need to be energy efficient.                                                                                                          & CoAP with protobufs      & CoAP was designed for resource and energy contrained devices. Protobufs offer the ability to compress messages efficiently and thus further reduce the energy consumption.                                                     & \textbackslash{}cref\{edgeIoT\}    \\
127 & Automatic updates                       & Should         & The edge device needs to be able to update the IoT device. The update process is intiated in the cloud. The operator does not have to do configurations locally (on the edge)              & Kubernetes + containers  & Kubernetes can schedule a pod on the node. The pod then loads the application code to the device, either OTA or cable.                                                                                                         & \textbackslash{}cref\{edgeIoT\}    \\
128 & OTA updates                             & Should         & The updates need to be able to support OTA updates.                                                                                                                                        & Esspresif OTA            & The manufacturer of the esp32 provides an examplary implementation of OTA updates.                                                                                                                                             & \textbackslash{}cref\{edgeIoT\}    \\
129 & Verified updates                        & Would          & The IoT device updates have to be verified.                                                                                                                                                & Secure images            & The IoT device compares the provided hash to the calculated image hash.                                                                                                                                                        & \textbackslash{}cref\{edgeIoT\}   
\end{longtable}
% \end{table}
\clearpage