\subsubsection{Kubernetes} \label{kubernetesStandardization efforts}
Kubernetes is the de-facto standard for container orchestration and the main technology used in this thesis. It is a highly complex tool and offers many  configurations, thus understanding the fundamentals is highly important. A deep understanding of Kubernetes resources also helps in understanding the current shortcoming concerning the edge. Kubernetes was designed from the ground up to be extensible, so the question is not if Kubernetes could do something, but rather if there is an existing implementation.

This section covers five important aspects of Kubernetes. First, single-cluster vs multi-cluster. Second, the core components of Kubernetes, mainly the kubelet, together with other resource configurations. Third, the optimal deployment strategy, how to control and secure resources and how to select nodes. Fourth,  how to do load balancing and, finally, how to do traffic control and shaping.\\[5mm]
% \vspace{0.5mm} \ \\
\textbf{\textit{Single vs. Multi-Cluster}}\\
\input{sections/2-extendedSota/kubernetes/k8sStuff/singleVsMultiCluster.tex}
% \vspace{0.5mm} \ \\
\textbf{\textit{Core Components}}\\
\input{sections/2-extendedSota/kubernetes/k8sStuff/coreComponents.tex}
% \vspace{0.5mm} \ \\
\textbf{\textit{Deployment Strategies}}\\
\input{sections/2-extendedSota/kubernetes/k8sStuff/deploymentStrategies.tex}
\\[5mm]
\textbf{\leftskip25mm\textit{Load Balancing}}\\
\input{sections/2-extendedSota/iotEdgeProblems/loadBalancing.tex}
\textbf{\leftskip25mm\textit{Traffic Control and Shaping}}\\
\input{sections/2-extendedSota/iotEdgeProblems/trafficShaping.tex}

\comment{
Removed section: Security and Recommendations
IIoT and the smartphone revolution have accelerated the need for fog computing and the industry is set to develop a container based orchestration tool, tightly integrated with Kubernetes. 
IIoT has accelerated the need for fog computing and the industry is set to develop a container based orchestration tool, tightly integrated with Kubernetes. The Kubernetes IoT edge working group was set up specifically to find the optimal Kubernetes strategy for the edge. However, it is not clear, whether the solution will be Kubernetes itslef or a more specialized tool. In this thesis I will argue that Kubernetes is the way forward as it already posses many of the features that are need for the edge.\\ 
}