\clearpage
\section{Conclusion and Future Outlook}
As a system administator it is hard to describe what it means to have a system that works for you. Traditionally, deploying or updating an application meant locally updating the application on each individual edge device. A tedious and time consuming task.

Having clearly defined APIs to tell the system what to do is a blessing. With Kubernetes deploying and updating applications can be done centrally via the configuration of API resources. The administrator tells the system what he wants and the system executes it for him. In the case of failure Kubernetes actively tries to recover from the failure and notifies the administrator. These and more are the advantages Kubernetes offers and the reason it is so popular in the cloud.

But it is not without its flaws. As Kelsey Hightower, a Kubernetes developer advocate at Google, said during KubeCon 2017: ``If you’re new to Kubernetes, it will set you free. But first it will piss you off''\cite{KubernetesPissYouOff:online}. From the experience of this thesis, this is more than true. Understanding Kubernetes, let alone containers, can be challenging. Understanding and implementing industry best practices, like scratch containers, using the image digest and Helm for resource deployments can be daunting tasks. But once, the barrier of understanding and using Kubernetes and its tools is broken, Kubernetes opens up a new world of possibilities for developers to manage resources in a cluster.

Updating an application on remote devices like the RPi to add new features and security is as easy as pushing a button. Additionally, rules can be defined to tightly control the system. Kubernetes offers rules for resource consumption, developer access networking and more. In this project alone, Kubernetes already simplified the orchestrating and managing of only one edge device. In a multi-node edge architecture these advantages will grow exponentially.

If edge devices, especially based on ARM, can be integrated as first class citizen in the Kubernetes developer community, it has a huge potential to become the de-facto standard for edge computing.

However, a few issues have to be worked out before Kubernetes should be used for production services on the edge. Istio needs better support for ARM. It is a crucial tool for fog computing as it allows automatic encryption between the nodes inside a cluster. A Kubernetes wide standard has to be implemented to deal with connection losses, retrials and longer timeouts to enable edge devices to function without a stable connection. One such solution is multi-cluster via KubeFed, but this feature is still in alpha version. The IoT community needs to come together and try to reduce the number of IoT protocols so that specific protocols can be tightly integrated into Kubernetes.  

The Kubernetes IoT Edge working group\cite{IntroducingDejanBosanac:KubernetesIoTEdgeWorkingGroup} is a step in the right direction to funnel the industry effort and explore the possibilities of Kubernetes for the edge. However, solutions which are tightly integrated into Kubernetes but do not run Kubernetes itself are going to have a hard time. Developers are going to expect the same experience and tools from their edge devices as from the cloud. Based on the current literature and the outcome of this thesis Kubernetes can be expected to take over the other projects and become the de-facto standard for edge and fog orchestration. To accelerate the development edge support has to be promoted to a first class citizen in Kubernetes. The testing servers should support and test all Kubernetes code on ARM. The Kubernetes installer needs a new flag for less powerful devices, e.g. \textit{--edge=true}, which would automatically set the kubectl into powersave mode (e.g. reduce the housekeeping rate and more). It is time to look over the edge of the cloud and enable a common building ground as close to the IoT and mobile devices as possible.

This thesis led to code commits to Istio as well as to the Kubeedge project. I would like to continue the work on the envoy proxy and expand on the services implemented in this thesis. Additionally, I would like to explore first hand the possibilities of multi-cluster architectures on the edge. It will be interesting to see how fast edge developers will embrace Kubernetes and create new tools for edge first and cloud second.
I will end this thesis with a quote from the CEO of the Eclipse Foundation summarizing the state of Kubernetes in 2019 on the edge:
\begin{displayquote}
\textit{\textbf{\Huge{``}}}
\textit{\large{
This is just getting started and this is a process — and not an event.\cite{ioFogMainBlog:online}
}}
\textit{\textbf{\Huge{''}}}
\\[1pt]
\raggedleft{{\rm --- Mike Milinkovich, CEO of Eclipse Foundation}}
\end{displayquote}
